Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-20 ms.tex
plotting results of subarray size test with no background aperture. Trying to understand the confusing results.

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_stripe128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
\caption{The subarray size tests show very similar precision levels with a horizontal aperture.}\label{fig:subarraySizes}
\end{figure*}

>>>>

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_stripe128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
{\gridline{\fig{azlab_ratio_tser_subarraySize_256.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_subarraySize_128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_subarraySize_064.pdf}{0.33\textwidth}{SUBGRISM64}}}
\caption{The subarray size tests show very similar precision levels with a background aperture horizontally displayed from the source aperture (top row).
If no background subtraction is done, paradoxically, the tallest subgrism (fewest groups) is the most stable. \textbf{\textcolor{red}{How does this make sense? Did I possibly change how the side reference pix correction was done between the 3 tests?}}}\label{fig:subarraySizes}
\end{figure*}
